Trajectoires de biodiversité en forêt tropicale exploitée

### 2018-03-13 index.Rmd
Form

<!-- knitr and R options (packages, ...) --> 
```{r Options, echo=FALSE, message=FALSE}
knitr::opts_chunk$set(cache=F, warning=FALSE, fig.env='SCfigure', out.width='80%', fig.asp=.75, fig.align='center')
# Installation of packages if necessary and loading
Library <- function(Packages) {
  InstallAndLoad <- function(Package) {
    if (!Package %in% installed.packages()[, 1]) {install.packages(Package)}
    require(Package, character.only = TRUE)
  }
  invisible(sapply(Packages, InstallAndLoad))
}
# Add necessary packages here
Packages <- c("bookdown", "knitr", "rmarkdown")

>>>>

<!-- knitr and R options (packages, ...) --> 
```{r Options, echo=FALSE, message=FALSE}
knitr::opts_chunk$set(cache=F, warning=FALSE, fig.env='SCfigure', out.width='80%', fig.asp=.75, fig.align='center')
# Installation of packages if necessary and loading
Library <- function(Packages) {
  InstallAndLoad <- function(Package) {
    if (!Package %in% installed.packages()[, 1]) {install.packages(Package)}
    require(Package, character.only = TRUE)
  }
  invisible(sapply(Packages, InstallAndLoad))
}
# Add necessary packages here
Packages <- c("bookdown", "knitr", "rmarkdown", "kableExtra")
